---
title: "Exercise 1 & 2"
author: "Nuray Nasib"
date: "3/29/2022"
output: 
  prettydoc::html_pretty:
    theme: tactile
    highlight: vignette
---



# Exercise 1

Consider a [FizzBuzz problem](https://codegolf.stackexchange.com/questions/58615/1-2-fizz-4-buzz). The program should write numbers from 1 to 100, separated by a newline, but multiples of 3 and of 5 should be replaced with "Fizz" and "Buzz" respectively. For numbers which are multiples of both 3 and 5 print "FizzBuzz". Here are some solutions, which are not readable:

Python: `for i in range(100):print(int(i%3/2)*'Fizz'+int(i%5/4)*'Buzz'or-~i)`
R: `x=y=1:100;y[3*x]='Fizz';y[5*x]='Buzz';y[15*x]='FizzBuzz';write(y[x],1)`

Write a readable and working solution in your preferred language.


 Solution:
 
```{r}
library(fizzbuzzR)

fizzbuzz(start = 1, end = 100, mod1 = 3, mod2 = 5)
```


# Exercise 2

1. Write a function which takes *n* (float or integer) as a parameter and returns the largest Fibonacci number smaller than *n*. The function should be documented, with type hints, and appropriate comments.

 Solution: 

```{r}
recurse_fibonacci <- function(n) {
if(n <= 1) {
return(n)
} else {
return(recurse_fibonacci(n-1) + recurse_fibonacci(n-2))
}
}
nterms = as.integer(readline(prompt="How many terms? "))
if(nterms <= 0) {
print("Plese enter a positive integer")
} else {
print("Fibonacci sequence:")
for(i in 0:(nterms-1)) {
print(recurse_fibonacci(i))
}
}
```


2. Write a function which reverses digits in an integer number (for example 7245 -> 5427). The function should be documented, with type hints, and appropriate comments.

 
 Solution:

```{r}
{
    n = as.integer(readline(prompt = 'Enter a number : '))
    rev = 0
    
     while (n > 0) {
     r = n %% 10.
     rev = rev * 10 + r
     n = n %/% 10}

     print(paste('Reverse number is : ', rev))
}
```




